Accuracy in Parameter Estimation and Simulation Approaches for Sample Size Planning with Multiple Stimuli

### 2023-12-28 manuscript_draft.Rmd
all the things!

```{r scale-size-figure, echo = F, fig.cap="Simulated pilot sample size and final projected sample size to achieve 80%, 85%, 90%, and 95% of items below threshold. These values are averaged over all other variables including decile. Black dots represent original sample size for reference. "}

@@

ggplot(summary_long %>% 
         group_by(original_n, power, scale_size) %>% 
         summarize(sample_size_avg = mean(sample_size)),
       aes(original_n, sample_size_avg, color = scale_size)) + 
  geom_point() + 
  geom_point(aes(original_n, original_n), color = "black") + 
  geom_line() + 
  geom_line(aes(original_n, original_n), color = "black") + 
  theme_linedraw(base_size = 15) + 
  xlab("\nPilot Sample Size") + 
  ylab("Projected Sample Size\n") + 
  scale_color_manual(name = "Scale Size",
                     values = c(plot_colors)) +
  facet_wrap(~power,
             labeller = labeller(power = power.labs))+
  theme_bw()
```

@@

```{r scale-skew-figure, echo = F, fig.cap="Simulated pilot sample size and final projected sample size to achieve 80%, 85%, 90%, and 95% of items below threshold. In comparison to Figure 1, this figure shows projected sample size for ceiling versus normal distributions on each scale. All other variables are averaged together, and black dots represent original sample size for reference." }

ggplot(summary_long %>% 
         group_by(original_n, power, data_type) %>% 
         summarize(sample_size_avg = mean(sample_size)),
       aes(original_n, sample_size_avg, color = data_type)) + 
  geom_point() + 
  geom_point(aes(original_n, original_n), color = "black") + 
  geom_line() + 
  geom_line(aes(original_n, original_n), color = "black") + 
  theme_linedraw(base_size = 15) + 
  xlab("\nPilot Sample Size") + 
  ylab("Projected Sample Size\n") + 
  scale_color_manual(name = "Scale Skew",
                     values = c(plot_colors)) +
  facet_wrap(~power,
             labeller = labeller(power = power.labs))+
  theme_bw()
```

@@

```{r scale-hetero-figure, echo = F, fig.cap="Simulated pilot sample size and final projected sample size to achieve 80%, 85%, 90%, and 95% of items below threshold. In comparison to Figure 1 and 2, this figure shows projected sample size or differing amounts of heterogeneity on each scale. All other variables are averaged together, and black dots represent original sample size for reference."}

ggplot(summary_long %>% 
         group_by(original_n, power, variability) %>% 
         summarize(sample_size_avg = mean(sample_size)),
       aes(original_n, sample_size_avg, color = variability)) + 
  geom_point() + 
  geom_point(aes(original_n, original_n), color = "black") + 
  geom_line() + 
  geom_line(aes(original_n, original_n), color = "black") + 
  theme_linedraw() + 
  xlab("Pilot Sample Size") + 
  ylab("Projected Sample Size") + 
  scale_color_manual(name = "Item Heterogeneity",
                     values = c(plot_colors)) +
  facet_wrap(~power,
             labeller = labeller(power = power.labs))+
  theme_bw()
```

@@

```{r corrected-figure, echo = F, fig.cap="Corrected projected sample sizes for variability and power levels to achieve 80%, 85%, 90%, and 95% of items below threshold. All other variables are averaged together, and black dots represent original sample size for reference."}

decay <- 1-sqrt((summary_long$original_n-20)/summary_long$original_n)^log2(summary_long$original_n)
summary_long$new_sample <- summary_long$sample_size*decay
ggplot(summary_long %>% 
         group_by(original_n, power, variability) %>% 
         summarize(sample_size_avg = mean(sample_size),
                   new_sample_size_avg = mean(new_sample)),
       aes(original_n, new_sample_size_avg, color = variability)) + 
  geom_line(aes(original_n, original_n), color = "black") +
  geom_point(aes(original_n, original_n), color = "black") + 
  geom_point() + 
  geom_line() + 
  xlab("\nPilot Sample Size") + 
  ylab("Projected Sample Size\n") + 
  scale_color_manual(name = "Item Heterogeneity",
                     values = c(plot_colors)) +
  facet_wrap(~power,
             labeller = labeller(power = power.labs))+
  theme_bw()
```

@@

```{r decile40-figure, fig.cap = "Comparison of the cutoffs for 40% deciles across heterogeneity (columns), powering of items (rows), and scale size (color)."}
summary_long %>% 
  filter(name == "Decile 40") %>% 
  group_by(variability, original_n, scale_size, name, power) %>% 
  summarize(new_sample = mean(new_sample)) %>% 
  ggplot(., aes(original_n, new_sample, color = scale_size)) + 
  geom_point(aes(original_n, original_n), color = "black") + 
  geom_line(aes(original_n, original_n), color = "black") + 
  geom_point() + 
  geom_line() + 
  theme_classic(base_size = 10) + 
  facet_grid(power~ variability,
             labeller = labeller(power = power.labs)) +
  ggtitle("Results for 40% deciles") +
  xlab("\nPilot Sample Size") + 
  ylab("Corrected Sample Size\n") + 
  scale_color_manual(name = "Scale Size",
                     values = c(plot_colors)) + 
  theme_bw() +
  theme(legend.position="bottom")

@@

```{r decile50-figure, fig.cap = "Comparison of the cutoffs for 50% deciles across heterogeneity (columns), powering of items (rows), and scale size (color)."}
summary_long %>% 
  filter(name == "Decile 50") %>% 
  group_by(variability, original_n, scale_size, name, power) %>% 
  summarize(new_sample = mean(new_sample)) %>% 
  ggplot(., aes(original_n, new_sample, color = scale_size)) + 
  geom_point(aes(original_n, original_n), color = "black") + 
  geom_line(aes(original_n, original_n), color = "black") + 
  geom_point() + 
  geom_line() +
  theme_classic(base_size = 10) + 
  facet_grid(power~ variability,
             labeller = labeller(power = power.labs)) + 
  ggtitle("Results for 50% deciles") +
  xlab("\nPilot Sample Size") + 
  ylab("Corrected Sample Size\n") + 
  scale_shape_discrete(name = "Scale Size") +
  scale_color_manual(name = "Cutoff Decile",
                     values = c(plot_colors)) + 
  theme_bw() +
  theme(legend.position="bottom")

@@

apa_table(table_correction_applied, 
          caption = "Applied Correction for Each Proposed Sample Size", 
          font_size = "footnotesize")
```

>>>>

```{r scale-size-figure, echo = F, fig.cap="Simulated pilot sample size and final projected sample size to achieve 80%, 85%, 90%, and 95% of items below threshold. These values are averaged over all other variables including decile. Black dots represent original sample size for reference. ", fig.height=6, fig.width=8}

@@

ggplot(summary_long %>% 
         group_by(original_n, power, scale_size) %>% 
         summarize(sample_size_avg = mean(sample_size)),
       aes(original_n, sample_size_avg, color = scale_size)) + 
  geom_point() + 
  geom_point(aes(original_n, original_n), color = "black") + 
  geom_line() + 
  geom_line(aes(original_n, original_n), color = "black") + 
  theme_linedraw(base_size = 15) + 
  xlab("\nPilot Sample Size") + 
  ylab("Projected Sample Size\n") + 
  scale_color_manual(name = "Scale Size",
                     values = c(plot_colors)) +
  facet_wrap(~power,
             labeller = labeller(power = power.labs))+
  theme_bw() +
  theme(legend.position="bottom")
```

@@

```{r scale-skew-figure, echo = F, fig.cap="Simulated pilot sample size and final projected sample size to achieve 80%, 85%, 90%, and 95% of items below threshold. In comparison to Figure 1, this figure shows projected sample size for ceiling versus normal distributions on each scale. All other variables are averaged together, and black dots represent original sample size for reference.", fig.height=6, fig.width=8 }

ggplot(summary_long %>% 
         group_by(original_n, power, data_type) %>% 
         summarize(sample_size_avg = mean(sample_size)),
       aes(original_n, sample_size_avg, color = data_type)) + 
  geom_point() + 
  geom_point(aes(original_n, original_n), color = "black") + 
  geom_line() + 
  geom_line(aes(original_n, original_n), color = "black") + 
  theme_linedraw(base_size = 15) + 
  xlab("\nPilot Sample Size") + 
  ylab("Projected Sample Size\n") + 
  scale_color_manual(name = "Scale Skew",
                     values = c(plot_colors)) +
  facet_wrap(~power,
             labeller = labeller(power = power.labs))+
  theme_bw() +
  theme(legend.position="bottom")
```

@@

```{r scale-hetero-figure, echo = F, fig.cap="Simulated pilot sample size and final projected sample size to achieve 80%, 85%, 90%, and 95% of items below threshold. In comparison to Figure 1 and 2, this figure shows projected sample size or differing amounts of heterogeneity on each scale. All other variables are averaged together, and black dots represent original sample size for reference.", fig.height=6, fig.width=8}

ggplot(summary_long %>% 
         group_by(original_n, power, variability) %>% 
         summarize(sample_size_avg = mean(sample_size)),
       aes(original_n, sample_size_avg, color = variability)) + 
  geom_point() + 
  geom_point(aes(original_n, original_n), color = "black") + 
  geom_line() + 
  geom_line(aes(original_n, original_n), color = "black") + 
  theme_linedraw() + 
  xlab("Pilot Sample Size") + 
  ylab("Projected Sample Size") + 
  scale_color_manual(name = "Item Heterogeneity",
                     values = c(plot_colors)) +
  facet_wrap(~power,
             labeller = labeller(power = power.labs))+
  theme_bw() +
  theme(legend.position="bottom")
```

@@

```{r corrected-figure, echo = F, fig.cap="Corrected projected sample sizes for variability and power levels to achieve 80%, 85%, 90%, and 95% of items below threshold. All other variables are averaged together, and black dots represent original sample size for reference.", fig.height=6, fig.width=8}

decay <- 1-sqrt((summary_long$original_n-20)/summary_long$original_n)^log2(summary_long$original_n)
summary_long$new_sample <- summary_long$sample_size*decay
ggplot(summary_long %>% 
         group_by(original_n, power, variability) %>% 
         summarize(sample_size_avg = mean(sample_size),
                   new_sample_size_avg = mean(new_sample)),
       aes(original_n, new_sample_size_avg, color = variability)) + 
  geom_line(aes(original_n, original_n), color = "black") +
  geom_point(aes(original_n, original_n), color = "black") + 
  geom_point() + 
  geom_line() + 
  xlab("\nPilot Sample Size") + 
  ylab("Projected Sample Size\n") + 
  scale_color_manual(name = "Item Heterogeneity",
                     values = c(plot_colors)) +
  facet_wrap(~power,
             labeller = labeller(power = power.labs))+
  theme_bw() +
  theme(legend.position="bottom")
```

@@

```{r decile40-figure, fig.cap = "Comparison of the cutoffs for 40% deciles across heterogeneity (columns), powering of items (rows), and scale size (color).", fig.height=8, fig.width=8}
summary_long %>% 
  filter(name == "Decile 40") %>% 
  group_by(variability, original_n, scale_size, name, power) %>% 
  summarize(new_sample = mean(new_sample)) %>% 
  ggplot(., aes(original_n, new_sample, color = scale_size)) + 
  geom_point(aes(original_n, original_n), color = "black") + 
  geom_line(aes(original_n, original_n), color = "black") + 
  geom_point() + 
  geom_line() + 
  theme_classic(base_size = 10) + 
  facet_grid(power~ variability,
             labeller = labeller(power = power.labs)) +
  ggtitle("Results for 40% deciles") +
  xlab("\nPilot Sample Size") + 
  ylab("Corrected Sample Size\n") + 
  scale_color_manual(name = "Scale Size",
                     values = c(plot_colors)) + 
  theme_bw() +
  theme(legend.position="bottom")

@@

```{r decile50-figure, fig.cap = "Comparison of the cutoffs for 50% deciles across heterogeneity (columns), powering of items (rows), and scale size (color).", fig.height=8, fig.width=8}
summary_long %>% 
  filter(name == "Decile 50") %>% 
  group_by(variability, original_n, scale_size, name, power) %>% 
  summarize(new_sample = mean(new_sample)) %>% 
  ggplot(., aes(original_n, new_sample, color = scale_size)) + 
  geom_point(aes(original_n, original_n), color = "black") + 
  geom_line(aes(original_n, original_n), color = "black") + 
  geom_point() + 
  geom_line() +
  theme_classic(base_size = 10) + 
  facet_grid(power~ variability,
             labeller = labeller(power = power.labs)) + 
  ggtitle("Results for 50% deciles") +
  xlab("\nPilot Sample Size") + 
  ylab("Corrected Sample Size\n") + 
  scale_shape_discrete(name = "Scale Size") +
  scale_color_manual(name = "Cutoff Decile",
                     values = c(plot_colors)) + 
  theme_bw() +
  theme(legend.position="bottom")

@@

apa_table(table_correction_applied, 
          caption = "Applied Correction for Each Proposed Sample Size", 
          font_size = "scriptsize",
          col.names = c("Formula", "Intercept", 
                                        "Proj SS", "Pilot SS", 
                                        "Log Proj SS", "Log Pilot SS", 
                                        "Log Power", "Prop Var", 
                                        "Log Prop Var", "Power", 
                        "Loss", "Cor SS"),
          landscape = TRUE,
          note = "SS = Sample Size, Proj = Projected, Prop = Proportion, Var = Variance, Cor = Corrected")
```

### 2023-12-28 manuscript_draft.tex
all the things!

A recent review of power analyses found - across behavioral, cognitive, and social science journal articles - researchers did not provide enough information to understand their power analyses and often chose effect sizes that were unjustified (Beribisky, 2019). One solution to this power analysis problem is the plethora of tools made available for researchers to make power computations accessible to non-statisticians; however, a solid education in power is necessary to use these tools properly. G*Power is one of the most popular free power software options (Erdfelder et al., 1996; Faul et al., 2007) that provides a simple point and click graphical user interface for power calculations (however, see Brysbaert, 2019). Web-based tools have also sprung up for overall and statistical test specific sample size planning including \url{https://powerandsamplesize.com}, \url{https://jakewestfall.shinyapps.io/pangea/}, \url{https://pwrss.shinyapps.io/index/}, and \url{https://designingexperiments.com} (Anderson et al., 2017). \emph{R}-coding based packages, such as \emph{pwr} (Champely et al., 2017), \emph{faux} (DeBruine, 2021), \emph{simr} (Green \& MacLeod, 2016), \emph{mixedpower} (Kumle \& DejanDraschkow, 2020), and \emph{SimDesign} (Chalmers \& Adkins, 2020), can be used to examine power and plan sample sizes, usually with simulation. Researchers must be careful using any toolkit, as errors can occur with the over-reliance on software (e.g., it should not be a substitute for critical thinking, Nuijten et al., 2016). Additionally, many tools assume data normality, place an overemphasis on statistical significance, and may rely on simplified assumptions that do not reflect the actual data. When computing sample size estimates, it is important to remember that these values are estimations, not exact calculations guaranteed to produce a specific result (Batterham \& Atkinson, 2005). For example, it is hard to accurately estimate all parameters from a study, and if any were incorrect, then the sample size estimate tied to that specific level of power may be incorrect (Albers \& Lakens, 2018).

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{2}
\tightlist
\item
  Sample, with replacement, from your pilot data using sample sizes starting at a value that you consider the minimal sample size per item and increase in small units up to a value that you consider the maximum sample size. We will demonstrate example maximum sample sizes based on the data simulation below; however, a practical maximum sample size may be determined by time (e.g., one semester data collection) or resources (e.g., 200 participants worth of funding). As for the minimal sample size, we suggest using 20 as a reasonable value for simulation purposes. For each sample size simulation, calculate the standard error for each item. Use multiple simulations (e.g., n = 500 to 1000) to avoid issues with random sampling variability.
\end{enumerate}

@@

The second dataset includes a large scale dataset with response latencies, the English Lexicon Project {[}ELP; Balota et al. (2007){]}. The ELP consists of lexical decision response latencies for written English words and pseudowords. In a lexical decision task, participants simply select ``word'' for real words (e.g., \emph{dog}) and ``nonword'' for pseudowords (e.g., \emph{wug}). The trial level data is available here: \url{https://elexicon.wustl.edu/}. Critically, in each of these datasets, the individual trial level data for each item is available to simulate and calculate standard errors on. Data that has been summarized could potentially be used, as long as the original standard deviations for each item were present. From the mean and standard deviation for each item, a simulated pilot dataset could be generated for estimating new sample sizes. All code to estimate sample sizes is provided on our OSF page, and this manuscript was created with a \emph{papaja} (Aust et al., 2022) formatted Rmarkdown document.

@@

\emph{Step 1}. The concreteness ratings data includes 27031 concepts that were rated for their concreteness. We randomly selected \emph{n} = 20 abstract words (\(M_{Rating}\) \textless= 2) and \emph{n} = 20 concrete words (\(M_{Rating}\) \textgreater= 4). In the original study, not every participant rated every word, which created uneven sample sizes for each word. Further, participants were allowed to indicate they did not know a word, and those responses were set to missing data. In our sample of 40 words, the average pilot sample size was 28.52 (\emph{SD} = 1.80), and we will use 29 as our pilot sample size for this example.

We first filtered the ELP data to the same real words as the concreteness subset selected above, and this data includes 27031 real words. The average pilot sample size for this random sample was 32.67 (\emph{SD} = 0.57), and \emph{n} = 33 will be our pilot size for this example.

@@

In this section, we simulate what a researcher might do if they follow our suggested application of AIPE to sample size planning based on well measured items. Assuming that each pilot sample represents a dataset that a researcher has collected (Step 1), the standard errors for each item were calculated to mimic the AIPE procedure of finding an appropriately small confidence interval, as SE functions as the main component of the formula for normal distribution confidence intervals. Standard errors were calculated at each decile of the items up to 90\% (i.e., 0\% smallest SE, 10\% \ldots, 90\% largest SE). The lower deciles would represent a strict criterion for accurate measurement, as many items would need smaller SEs to meet cutoff scores, while the higher deciles would represent less strict criteria for cutoff scores(Step 2).

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-beribisky2019}{}}%
Beribisky, N. (2019). \emph{A Multi-Faceted Mess: A Review of Statistical Power Analysis in Psychology Journal Articles}. \url{https://yorkspace.library.yorku.ca/xmlui/handle/10315/36719}

@@

\leavevmode\vadjust pre{\hypertarget{ref-silberzahn2018many}{}}%
Silberzahn, R., Uhlmann, E. L., Martin, D. P., Anselmi, P., Aust, F., Awtrey, E., Bahník, Š., Bai, F., Bannard, C., Bonnier, E., \& others. (2018). Many analysts, one data set: Making transparent how variations in analytic choices affect results. \emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(3), 337356.

>>>>

A recent review of power analyses found - across behavioral, cognitive, and social science journal articles - researchers did not provide enough information to understand their power analyses and often chose effect sizes that were unjustified (Beribisky et al., 2019). One solution to this power analysis problem is the plethora of tools made available for researchers to make power computations accessible to non-statisticians; however, a solid education in power is necessary to use these tools properly. G*Power is one of the most popular free power software options (Erdfelder et al., 1996; Faul et al., 2007) that provides a simple point and click graphical user interface for power calculations (however, see Brysbaert, 2019). Web-based tools have also sprung up for overall and statistical test specific sample size planning including \url{https://powerandsamplesize.com}, \url{https://jakewestfall.shinyapps.io/pangea/}, \url{https://pwrss.shinyapps.io/index/}, and \url{https://designingexperiments.com} (Anderson et al., 2017). \emph{R}-coding based packages, such as \emph{pwr} (Champely et al., 2017), \emph{faux} (DeBruine, 2021), \emph{simr} (Green \& MacLeod, 2016), \emph{mixedpower} (Kumle \& DejanDraschkow, 2020), and \emph{SimDesign} (Chalmers \& Adkins, 2020), can be used to examine power and plan sample sizes, usually with simulation. Researchers must be careful using any toolkit, as errors can occur with the over-reliance on software (e.g., it should not be a substitute for critical thinking, Nuijten et al., 2016). Additionally, many tools assume data normality, place an overemphasis on statistical significance, and may rely on simplified assumptions that do not reflect the actual data. When computing sample size estimates, it is important to remember that these values are estimations, not exact calculations guaranteed to produce a specific result (Batterham \& Atkinson, 2005). For example, it is hard to accurately estimate all parameters from a study, and if any were incorrect, then the sample size estimate tied to that specific level of power may be incorrect (Albers \& Lakens, 2018).

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{2}
\tightlist
\item
  Sample, with replacement, from your pilot data using sample sizes starting at a value that you consider the minimal sample size per item and increase in small units up to a value that you consider the maximum sample size. We will demonstrate example maximum sample sizes based on the data simulation below; however, a practical maximum sample size may be determined by time (e.g., one semester data collection) or resources (e.g., 200 participants worth of funding). As for the minimal sample size, we suggest using 20 as a reasonable value for simulation purposes. For each sample size simulation, calculate the standard error for each item. Use multiple simulations (e.g., \emph{n} = 500 to 1000) to avoid issues with random sampling variability.
\end{enumerate}

@@

The second dataset includes a large scale dataset with response latencies, the English Lexicon Project (ELP, Balota et al., 2007). The ELP consists of lexical decision response latencies for written English words and pseudowords. In a lexical decision task, participants simply select ``word'' for real words (e.g., \emph{dog}) and ``nonword'' for pseudowords (e.g., \emph{wug}). The trial level data is available here: \url{https://elexicon.wustl.edu/}. Critically, in each of these datasets, the individual trial level data for each item is available to simulate and calculate standard errors on. Data that has been summarized could potentially be used, as long as the original standard deviations for each item were present. From the mean and standard deviation for each item, a simulated pilot dataset could be generated for estimating new sample sizes. All code to estimate sample sizes is provided on our OSF page, and this manuscript was created with a \emph{papaja} (Aust et al., 2022) formatted Rmarkdown document.

@@

\emph{Step 1}. The concreteness ratings data includes 27031 concepts that were rated for their concreteness. We randomly selected \emph{n} = 20 abstract words (\(M_{Rating}\) \textless= 2) and \emph{n} = 20 concrete words (\(M_{Rating}\) \textgreater= 4). In the original study, not every participant rated every word, which created uneven sample sizes for each word. Further, participants were allowed to indicate they did not know a word, and those responses were set to missing data. In our sample of 40 words, the average pilot sample size was 28.52 (\emph{SD} = 1.80), and we will use 29 as our pilot sample size for the concreteness ratings.

We first filtered the ELP data to the same real words as the concreteness subset selected above, and this data includes 27031 real words. The average pilot sample size for this random sample was 32.67 (\emph{SD} = 0.57), and \emph{n} = 33 will be our pilot size for the lexical decision task.

@@

In this section, we simulate what a researcher might do if they follow our suggested application of AIPE to sample size planning based on well measured items. Assuming that each pilot sample represents a dataset that a researcher has collected (Step 1), the standard errors for each item were calculated to mimic the AIPE procedure of finding an appropriately small confidence interval, as SE functions as the main component of the formula for normal distribution confidence intervals. Standard errors were calculated at each decile of the items up to 90\% (i.e., 0\% smallest SE, 10\% \ldots, 90\% largest SE). The lower deciles would represent a strict criterion for accurate measurement, as many items would need smaller SEs to meet cutoff scores, while the higher deciles would represent less strict criteria for cutoff scores (Step 2).

@@

\begin{lltable}

\begin{TableNotes}[para]
\normalsize{\textit{Note.} SS = Sample Size, Proj = Projected, Prop = Proportion, Var = Variance, Cor = Corrected}
\end{TableNotes}

\scriptsize{

\begin{longtable}{llllllllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:table-scores-updated}Applied Correction for Each Proposed Sample Size}\\
\toprule
Formula & Intercept & Proj SS & Pilot SS & Log Proj SS & Log Pilot SS & Log Power & Prop Var & Log Prop Var & Power & Loss & Cor SS\\
\midrule
\endfirsthead
\caption*{\normalfont{Table \ref{tab:table-scores-updated} continued}}\\
\toprule
Formula & Intercept & Proj SS & Pilot SS & Log Proj SS & Log Pilot SS & Log Power & Prop Var & Log Prop Var & Power & Loss & Cor SS\\
\midrule
\endhead
Formula & 206.59 & 0.37 & -0.77 & 27.54 & 2.58 & -66.15 & 16.40 & -1.37 & 1.09 & NA & NA\\
Concrete 80 & 1.00 & 45.00 & 29.00 & 5.49 & 4.86 & 6.32 & 0.14 & -2.82 & 80.00 & 39.63 & 42.56\\
Concrete 85 & 1.00 & 45.00 & 29.00 & 5.49 & 4.86 & 6.41 & 0.14 & -2.82 & 85.00 & 39.29 & 42.19\\
Concrete 90 & 1.00 & 50.00 & 29.00 & 5.64 & 4.86 & 6.49 & 0.14 & -2.82 & 90.00 & 45.30 & 48.65\\
Concrete 95 & 1.00 & 55.00 & 29.00 & 5.78 & 4.86 & 6.57 & 0.14 & -2.82 & 95.00 & 51.21 & 54.99\\
LDT 80 & 1.00 & 55.00 & 33.00 & 5.78 & 5.04 & 6.32 & 0.08 & -3.60 & 80.00 & 48.79 & 61.05\\
LDT 85 & 1.00 & 70.00 & 33.00 & 6.13 & 5.04 & 6.41 & 0.08 & -3.60 & 85.00 & 63.54 & 79.51\\
LDT 90 & 1.00 & 90.00 & 33.00 & 6.49 & 5.04 & 6.49 & 0.08 & -3.60 & 90.00 & 80.87 & 101.20\\
LDT 95 & 1.00 & 130.00 & 33.00 & 7.02 & 5.04 & 6.57 & 0.08 & -3.60 & 95.00 & 110.48 & 138.25\\
\bottomrule
\addlinespace
\insertTableNotes
\end{longtable}

\end{lltable}

@@

\leavevmode\vadjust pre{\hypertarget{ref-beribisky2019}{}}%
Beribisky, N., Alter, U., \& Cribbie, R. (2019). \emph{A multi-faceted mess: A systematic review of statistical power analysis in psychology journal articles}. \url{https://doi.org/10.31234/osf.io/3bdfu}

@@

\leavevmode\vadjust pre{\hypertarget{ref-silberzahn2018many}{}}%
Silberzahn, R., Uhlmann, E. L., Martin, D. P., Anselmi, P., Aust, F., Awtrey, E., Bahník, Š., Bai, F., Bannard, C., Bonnier, E., \& others. (2018). Many analysts, one data set: Making transparent how variations in analytic choices affect results. \emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(3), 337356. \url{https://doi.org/10.1177/2515245917747646}
